A Survey Wearable Device Risk Perceptions

### 2015-01-03 wearables_survey.tex
Commented on Related Work

\section{Related Work}
In this section, we discuss related work which discusses emerging challenges related to ubiquitous computing, explores threats for smartphones, and studies user perceptions of threats and technologies.

\subsection{Ubiquitous Sensing}
Wearable devices, along with many other devices, are moving towards automated capture and ubiquitous  access~\cite{abowd2000charting}. More than ever, people will interact with sensors while carrying out daily activities, from a myriad of sources and for a variety of reasons: ``lifelogging'' devices to record their daily lives~\cite{hoyle2014privacy,dickie2004augmenting}, memory augmentation devices~\cite{chen2010augmenting,devaul2003memory,kalnikaite2010now}, smart homes that optimize living conditions~\cite{chan2008review,chan2009smart,edwards2001home}, devices that create augmented reality environments~\cite{azuma1997survey,azuma2001recent}, and even devices integrated into clothing \cite{anliker2001weararm}. The ubiquitous capture and storage of information naturally raises concerns about the preservation of privacy~\cite{palen2003unpacking}. Privacy in the field of ubiquitous computing relies on principles including notice, choice, and consent~\cite{langheinrich2001privacy}.

\subsection{Smartphones and Wearables Concerns}

There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro}. However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user. Felt et. al's study of smartphone user concerns \cite{Felt} was the first to investigate the security and privacy research landscape from a user study standpoint. The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges. To our knowledge, our work is the first of its kind to investigate user concerns for wearable devices.

\subsection{Risk Perception}

While evaluating which are the most pressing concerns for users, it is also important to take into account how users' perception of particular technology. A seminal risk-benefit analysis psychometric study by Fischoff \cite{Fischhoff} studied how 76 users perceived the risks and benefits of 30 activities and technologies. In our survey, we also explore how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.

>>>>

\section{Related Work}
In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.

\subsection{Ubiquitous Sensing}
{\color{red} This is plagiarized from our CHI paper! REWRITE!!! } Wearable devices, along with many other devices, are moving towards automated capture and ubiquitous  access~\cite{abowd2000charting}. More than ever, people will interact with sensors while carrying out daily activities, from a myriad of sources and for a variety of reasons: ``lifelogging'' devices to record their daily lives~\cite{hoyle2014privacy,dickie2004augmenting}, memory augmentation devices~\cite{chen2010augmenting,devaul2003memory,kalnikaite2010now}, smart homes that optimize living conditions~\cite{chan2008review,chan2009smart,edwards2001home}, devices that create augmented reality environments~\cite{azuma1997survey,azuma2001recent}, and even devices integrated into clothing \cite{anliker2001weararm}. The ubiquitous capture and storage of information naturally raises concerns about the preservation of privacy~\cite{palen2003unpacking}. Privacy in the field of ubiquitous computing relies on principles including notice, choice, and consent~\cite{langheinrich2001privacy}.

\subsection{Smartphones and Wearables Concerns}
{\color{red} Add way more details about Felt's study, so that it's clear how we borrowed the methodology, without the reader having to read that paper.}
There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro}. However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user. Felt et. al's study of smartphone user concerns \cite{Felt} was the first to investigate the security and privacy research landscape from a user study standpoint. The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges. To our knowledge, our work is the first of its kind to investigate user concerns for wearable devices.

\subsection{Technology Risk Perceptions}
{\color{red} Again, you need to add lots more about this paper, so that it's clear from your description what they did, and how we build upon it.}
While evaluating which are the most pressing concerns for users, it is also important to take into account how users' perception of particular technology. A seminal risk-benefit analysis psychometric study by Fischoff \cite{Fischhoff} studied how 76 users perceived the risks and benefits of 30 activities and technologies. In our survey, we also explore how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.
